---
name: Thach H.
surname: Pham
position: PhD, Asset Pricing
profilepic: "thach-vic.jpg"
headcolor: "1976D2"
address: |
  | Faculty of Finance & Banking, HCMC Open University, Vietnam
#phone: 
www: thachpham.wordpress.com
email: "phamhoangthach@gmail.com"
#twitter: 
github: pham-hoang-thach
linkedin: phamhoangthach
aboutme: "I like collaborative environments where I can learn from my peers. I have worked in a variety of roles ranging from financial  and data analyst to investment officer to researcher and lecturer. I am passionate about education and I believe that none of subject is too complex if the teacher is empathetic and willing to think of new approaches. In my PhD thesis, I have developed a framework for stock selection strategies based on mispricing and smart betas. This framework not only helps in explaining stock returns but also in evaluating the efficiency of stock markets and the performance of trading strategies. I love Linux and free and open-source software. I prefer literate programming, reproducible research, and plain text."
date: "`r format(Sys.time(), '%B %Y')`"
output: 
  vitae::awesomecv:
    page_total: true
header-includes:
   - \usepackage{svg}
   - \usepackage{float}
   - \usepackage{tabularx}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
options(tinytex.engine_args = '--shell-escape')
library(vitae)
library(here)
```

```{r functions}
readExcelSheets <- function(filename){
  # read all sheets in .xlsx 
  all <- readxl::excel_sheets(filename)
  
  # import each sheet into a list using readxl::read_excel
  list <- lapply(all, function(x) readxl::read_excel(filename, sheet = x))
  
  # save sheet name for each sheet (list)
  names(list) <- all
  
  # breaks up list and creates a dataframe for each sheet with df names matching sheet names
  list2env(list, envir = .GlobalEnv)
}
```

```{r load-data, message=F, results='hide'}
filename <- here::here("cv", "cv.xlsx")
readExcelSheets(filename)
```

<!--
# About me

  * I have worked in a variety of roles ranging from financial analyst to investment officer to researcher. I like collaborative environments where I can learn from my peers. 
  * I have a strong background in the finance literature and working knowledge of stock markets.
  * My research interests include asset pricing, portfolio optimisation, market efficiency, and trading strategies. 
 * I am passionate about literate programming and reproducible research. 
 * I prefer $\href{https://plain-text.co/}{\text{plain text}}$ & $\href{https://en.wikipedia.org/wiki/Free_and_open-source_software}{\text{FOSS (Free and open-source software)}}$. 
 -->
 
# Education

```{r}
education %>% 
  detailed_entries(what = degree,
                   when = year,
                   with = institution,
                   where = where,
                   why = details)
```

# Training

```{r}
training %>% 
  detailed_entries(what = training,
                   when = year,
                   with = institution,
                   where = where,
                   why = details)
```

# Achievements

```{r}
library(tibble)
tribble(
  ~Year, ~Type, ~Desc,
  "2018–2020", "Joint Victoria University and Vietnam International Education Development PhD Scholarship (VIED, 911)", "Tuition and Stipend Sponsorship",
  "", "", "",
  "2020", "Top 15% highest achieving students, Victoria University", "Awarded for the outstanding academic achievements",
  "", "", "",
  "2021", "Victoria University PhD Scholarship", "Tuition and Stipend Sponsorship",
  "", "", "",
  "2023", "Excellent PhD Thesis", "Awarded for the outstanding academic achievements",
) %>% 
  brief_entries(
    glue::glue("{Type}"),
    Year, 
    Desc
  )
```

# Skills

  * Presentation, Research and Teaching
  * Data Wrangling and Visualization
  * Statistical and Financial Modeling
  * Programming
  * Version Control
  * Linux and Open Source Software
  * Reporting and Writing
  * Personal Knowledge Management and Personal Productivity

# Tools

\begin{table}[H]
\begin{tabularx}{1\linewidth}{X X X}
\includesvg[width=30pt]{img/R} \href{https://cran.r-project.org/}{R} & \includesvg[width=30pt]{img/debian} \href{https://www.debian.org/}{Debian} & \includesvg[width=30pt]{img/python} \href{https://www.python.org/}{Python} \\
\includesvg[width=30pt]{img/markdown} \href{https://www.markdownguide.org/}{Markdown} & \includesvg[width=30pt]{img/emacs} \href{https://www.gnu.org/software/emacs/}{Emacs} & \includesvg[width=30pt]{img/unicorn} \href{https://orgmode.org/}{Org Mode} \\
\includesvg[width=30pt]{img/latex} \href{https://www.latex-project.org/}{LaTeX}& \includesvg[width=30pt]{img/zotero} \href{https://www.zotero.org/}{Zotero} & \includesvg[width=30pt]{img/git} \href{https://git-scm.com/}{Git}
\end{tabularx}
\end{table}

# Teaching

```{r}
teaching %>% 
  detailed_entries(what = role,
                   when = dates,
                   with = institution,
                   where = where,
                   why = details)
```

# Research Experience

```{r}
research %>% 
  detailed_entries(what = role,
                   when = dates,
                   with = institution,
                   where = where,
                   why = details)
```


# Industry Experience

```{r}
industry %>% 
  detailed_entries(what = role,
                   when = dates,
                   with = institution,
                   where = where,
                   why = details)
```

# Software

\noindent \textbf{Pham, T.H.} (2025). \textit{MCQ Balance Engine}. GitHub.  
\url{https://github.com/Pham-Hoang-Thach/mcq-balance-engine.git}

\noindent \textbf{Pham, T.H.} (2023). \textit{Emacs Configuration for Literate Programming}. GitHub.  
\url{https://github.com/Pham-Hoang-Thach/.emacs.d.git}

# Publications

```{r}
# library(dplyr)
# knitr::write_bib(c("vitae", "tibble"), "packages.bib")
# 
# bibliography_entries("packages.bib") %>%
#   arrange(desc(author$family), issued)
```

<!-- \setlength{\leftskip}{0cm} -->
<!-- **2023** -->

<!--\setlength{\leftskip}{1cm}-->
Võ Minh Long, Lê Ngọc Yến Ngân, **Phạm Hoàng Thạch** (2025). *Tác động của giới hạn tài chính đến nắm giữ tiền mặt của các doanh nghiệp phi tài chính*. Tạp chí Kinh Tế và Ngân Hàng Châu Á, 228, 71-85.

<!--\setlength{\leftskip}{1cm}-->
**Phạm Hoàng Thạch** (2025). *Đo lường thị trường hiệu quả qua các mô hình nhân tố—Nghiên cứu thực nghiệm tại Sở Giao Dịch Chứng Khoán Thành phố Hồ Chí Minh*. HCMCOUJS-Kinh Tế và Quản Trị Kinh Doanh, 20(1), 69–81.

<!--\setlength{\leftskip}{1cm}-->
**Pham, T.H.**, Phan, T.M.H. (2024). *Trading Stategies in the Ho Chi Minh Stock Exchange*. In Disruptive Technology and Business Continuity: Proceedings of The 5^th^ International Conference on Business (ICB 2023) (pp. 297–311). Springer Nature. 

<!--\setlength{\leftskip}{1cm}-->
**Phạm Hoàng Thạch** (2024). *Bước Đi Ngẫu Nhiên: Mô Phỏng Và Kiểm Tra Thị Trường Hiệu Quả Với R*. Hội thảo Ngành Tài Chính - Ngân hàng Việt Nam: Vượt thách thức, vững bước tiến, Khoa TC-NH, Đại học Mở TPHCM.

<!--\setlength{\leftskip}{1cm}-->
**Pham, T.H.**, Phan, T.M.H. (2023). *Trading Stategies in the Ho Chi Minh Stock Exchange*. The 5^th^ International Conference on Busines (ICB) [Conference Presentation].

<!--\setlength{\leftskip}{1cm}-->
Dương Quỳnh Nga, Phạm Hà, **Phạm Hoàng Thạch** (2023). *Quản lý danh mục đầu tư (HC)*. Tài liệu học tập. Đại học Mở Tp.HCM.

<!--\setlength{\leftskip}{1cm}-->
**Pham, T.H.** (2023). *Stock Selection for Trading Strategies Based on Risk Factors: A Study of The Ho Chi Minh Stock Exchange*. [PhD Thesis, Victoria University, Melbourne, Australia].

<!--\setlength{\leftskip}{1cm}-->
Dương Quỳnh Nga, Phạm Hà, **Phạm Hoàng Thạch** (2022). *Quản lý danh mục đầu tư*. Tài liệu học tập. Đại học Mở Tp.HCM. 

<!--\setlength{\leftskip}{1cm}-->
**Pham, T.H.**, Wickremasinghe, G., Kulendran, N. (2022). *An empirical study of the cross-section of stock returns on the Ho Chi Minh Stock Exchange (HSX) in Vietnam.* Working Paper.

<!--\setlength{\leftskip}{1cm}-->
**Pham, T.H.**, Wickremasinghe, G., Kulendran, N. (2022). *An empirical study of multifactor asset pricing models on the Ho Chi Minh Stock Exchange (HSX) in Vietnam.* Working Paper.

<!--\setlength{\leftskip}{1cm}-->
**Pham, T.H.** (2019). *A study of stock returns on the Ho Chi Minh Stock Exchange using ANOVA and multiple regressions.* Working Paper.

<!--\setlength{\leftskip}{1cm}-->
**Pham, T.H.** (2018). *An empirical study of the cross-section of stock returns on the Ho Chi Minh Stock Exchange.* [Year 1 Thesis, Victoria University, Melbourne, Australia]. 

<!--\setlength{\leftskip}{1cm}-->
**Phạm Hoàng Thạch**, Dương Quỳnh Nga (2018). *Quản lý danh mục đầu tư*. Slides bài giảng và video hướng dẫn môn học trực tuyến. Đại học Mở Tp.HCM. 

<!--\setlength{\leftskip}{1cm}-->
**Phạm Hoàng Thạch** (2006). *Xác định các ngành công nghiệp chủ lực của tỉnh Long An* [Luận văn đại học, Đại học Kinh tế Tp.HCM, Tp.HCM, Việt Nam]. 
